\documentclass{article}
\usepackage[margin=5em]{geometry}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{scrextend}
\usepackage[parfill]{parskip}

\titlespacing*{\section}{0pt}{10pt}{2pt}
\titlespacing*{\subsection}{0pt}{10pt}{2pt}
\titlespacing*{\subsubsection}{0pt}{10pt}{1pt}

\newcommand\CVEntry[3]{
  {\bf #1,} #2, {\it #3}
}
\newcommand\CVComment[4]{
  \CVEntry{#1}{#2}{#3}

  #4
}


\begin{document}

\begin{center}

{\large\bf Martin Erts\aa s}\\
\bigskip
martiert@gmail.com\\
+47 92 21 79 82\\
martiert @ github\\
Software Developer\\
Public Speaker\\
People Manager\\
\end{center}

\subsection*{SUMMARY}

\begin{multicols}{2}

  \begin{addmargin}[2em]{0em}
    \subsubsection*{Technology}

    \begin{addmargin}[1em]{0em}
      Developer of large, multithreaded systems for collaboration. Mainly working in C++
      with embedded Linux systems. Coded multiple lower level components to support various
      architectural changes and making the code more modular.
    \end{addmargin}

    \subsubsection*{Collaboration}

    \begin{addmargin}[1em]{0em}
      Experienced in initiatives to share code across several time zones, and across
      different work cultures.
    \end{addmargin}

    \subsubsection*{Processes}

    \begin{addmargin}[1em]{0em}
      Passionate about contributor happiness. Both created and changed systems and pipelines
      to make developers face less obstacles while doing their job.
    \end{addmargin}

    \subsubsection*{Learning}

    \begin{addmargin}[1em]{0em}
      Continuously striving to learn and understand new technologies, and develop both hard
      and soft skills.

      Also enjoy helping others develop the skills they need, either by doing talks/courses
      myself, or by using my contacts to get in external experts.
    \end{addmargin}

  \end{addmargin}

\end{multicols}

\subsection*{TECHNOLOGIES}

\begin{multicols}{2}

  \begin{itemize}
    \item C++ Programming language
    \item Python
    \item Git
    \item Linux operating system
    \item Linux userspace development
    \item Bash language
    \item Python asyncio and aiohttp library
  \end{itemize}
\end{multicols}

\subsection*{EMPLOYMENT}

\begin{addmargin}[2em]{0em}
  \CVComment{Software Technical Lead}{Cisco}{2023 - present}{
    Removed people management responsibilities to focus on the technical work, and especially
    technical leadership within my team and accross sites.}

  \CVComment{Software Engineering Manager}{Cisco}{2020 - 2023}{
    Taken on people management responsibilities for a group of people, both experienced and 
    unexperienced employees.}

  \CVComment{Training Responsible}{Cisco}{2019 - present}{
    Responsible for the training program for the Lysaker office, as well as the offices connected to
    it. Meaning groups in Ireland, London and North Carolina.}

  \CVEntry{Embedded C++ Developer}{Cisco}{2018 - present}

  \CVEntry{Embedded Android Developer}{Cisco}{2017 - 2018}{
    Focusing on the AOSP (Android Open Source Project), build tools and structure.
  }

  \CVEntry{Embedded C++ Developer}{Cisco}{2012 - 2017}

  \CVEntry{Windows and OS X C/C++ Developer}{Cisco}{2011 - 2012}

  \CVEntry{Informatics Teaching Assistant}{University of Oslo}{2008 - 2011}

  \CVEntry{Exam Grader in Numerical Calculations}{University of Oslo}{2010}

\end{addmargin}

\subsection*{COMMITTEE WORK}

\begin{addmargin}[2em]{0em}
  \CVEntry{Member of Agenda Committee}{NDC Security}{2022 - present}

  \CVEntry{Leader of Agenda Committee}{NDC TechTown}{2020 - present}

  \CVComment{Member of Agenda Committee}{NDC TechTown}{2019 - present}{
    NDC TechTown is a conference held in Kongsberg every year, which focuses on C++
    and embedded programming. The conference is organized by NDC Conferences. The
    agenda committee consists of people from the industry is responsible for
    selecting and getting a hold of speakers, as well as setting up the agenda.}

\end{addmargin}

\subsection*{PUBLIC SPEAKING}

\begin{addmargin}[2em]{0em}
  \CVEntry{Seccomp in practice}{NDC Security}{2023}

  \CVEntry{Sandboxing your Linux Application}{NDC Security}{2022}

  \CVEntry{Sandboxing your Linux Application}{ACCU}{2022}

  \CVEntry{Sandboxing your Linux Application}{NDC TechTown}{2021}

  \CVEntry{Securing Chromium In an Embedded Android Device}{Cisco Internal}{2020}

  \CVEntry{Sandboxing your Linux Application (1 day course)}{Cisco SecCon (Internal Conference)}{2020}

  \CVEntry{Using Android as OS for a single purpose system}{NDC TechTown}{2019}
\end{addmargin}


\subsection*{EDUCATION}

\begin{addmargin}[2em]{0em}
  \CVComment{The University of Oslo}{Oslo, Norway}{2009 - 2011}{
    Master of Science program, Department of Informatics (specialties in physics simulations on GPUs)}

  \CVComment{The University of Oslo}{Oslo, Norway}{2006 - 2009}{
    Bachelors degree, Department of Mathematics}
\end{addmargin}

\subsection*{SERVICE}

\begin{addmargin}[2em]{0em}
  \CVEntry{Contributor, Arduino assignments}{Kodeklubben.no}{2015 - 2017}

  \CVEntry{Teacher}{L\ae r Kidsa Koding}{2015}
\end{addmargin}

\end{document}
